Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-12-11 paper/manuscript.tex

\paragraph{Topologies} A critical first step in relative calculations is to select an approach to these calculations, determining whether to use a \emph{dual topology}, \emph{single topology}, or \emph{hybrid topology} approach to relative calculations.
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{paper/figures/fig4_topol/Fig4.pdf}
    \caption{top: single topology bottom: dual topology Figure adapted from \url{http://www.alchemistry.org/wiki/Constructing_a_Pathway_of_Intermediate_States}}
    \label{fig:fig4_topology}
\end{figure} 
The distinction between these can be illustrated by considering a hypothetical transformation from molecule A to molecule B, where both atoms share a common substructure but differ in their substituents; e.g. consider a transformation of benzene (A) to benzyl alcohol (B)~\ref{fig:fig4_topology}.
In this case the common substructure is the benzene ring, though perhaps may be larger depending on how it is defined, as we discuss below.
In single topology calculations, the overall transformation is set up to involve as few additional atoms as possible, so benzene would be typically changed into benzyl alcohol by changing one of the hydrogens into a carbon. To this new carbon you also find non-interacting atoms called ``dummy atoms'' (retaining their bonded interactions but not interacting with the rest of the system), which will become the two hydrogens attached to the new carbon and the OH group. Bond parameters as well as partial charges are adjusted accordingly. 
Thus, in a single topology calculation, atoms may change their type so relatively few dummy atoms are created. This is illustrated in fig.~\ref{fig:fig4_topology} (a). 
In contrast, in a dual topology free energy calculation, no atoms are allowed to change type~\cite{shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where atoms which are becoming dummy atoms or ceasing being dummy atoms are partially interacting (this state may or may not be well defined~\cite{mobley2014blind}  and culminating in a state where benzyl alcohol is present along with the additional dummy atoms which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig4_topology} (b) depicts how such a dual topology works.

@@

%%%%%%%%%%%%%%%% 
% end checklist:
\end{todolist}
\end{itemize}
\end{checklist_font}
\twocolumn
%%%%%%%%%%%%%%%%%
\clearpage

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and created figures \ref{fig:fig2_what_is_lambda},~\ref{fig:fig7_sampling_scheme},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} 
JS: created figures \ref{fig:fig1_what_is_alchemy}, \ref{fig:fig3_binding-thermodynamic-cycle}-\ref{fig:fig6_absolute-thermodynamic-cycle}, the checklist and contributed to general formatting discussions. 
% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.

>>>>

\paragraph{Topologies} A critical first step in relative calculations is to select an approach to these calculations, determining whether to use a \emph{dual topology}, \emph{single topology}, or \emph{hybrid topology} approach to relative calculations.
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig4_topol/Fig4.pdf}
    \caption{top: single topology bottom: dual topology Figure adapted from \url{http://www.alchemistry.org/wiki/Constructing_a_Pathway_of_Intermediate_States}}
    \label{fig:fig4_topology}
\end{figure} 
The distinction between these can be illustrated by considering a hypothetical transformation from molecule A to molecule B, where both atoms share a common substructure but differ in their substituents; e.g. consider a transformation of benzene (A) to benzyl alcohol (B)~\ref{fig:fig4_topology}.
In this case the common substructure is the benzene ring, though perhaps may be larger depending on how it is defined, as we discuss below.
In single topology calculations, the overall transformation is set up to involve as few additional atoms as possible, so benzene would be typically changed into benzyl alcohol by changing one of the hydrogens into a carbon. To this new carbon you also find non-interacting atoms called ``dummy atoms'' (retaining their bonded interactions but not interacting with the rest of the system), which will become the two hydrogens attached to the new carbon and the OH group. Bond parameters as well as partial charges are adjusted accordingly. 
Thus, in a single topology calculation, atoms may change their type so relatively few dummy atoms are created. This is illustrated in fig.~\ref{fig:fig4_topology} (a). 
In contrast, in a dual topology free energy calculation, no atoms are allowed to change type~\cite{shirts2012best}. This means that the benzene to benzyl alcohol transformation involves starting with benzene plus the non-interacting dummy atoms making up the hydroxy methyl group, then passing through an intermediate state where atoms which are becoming dummy atoms or ceasing being dummy atoms are partially interacting (this state may or may not be well defined~\cite{mobley2014blind}  and culminating in a state where benzyl alcohol is present along with the additional dummy atoms which was previously a corresponding hydrogen of the benzene. Fig.~\ref{fig:fig4_topology} (b) depicts how such a dual topology works.

@@

\begin{checklist}{Relative simulations}
\textbf{What are the main things I need to consider for an relative alchemical free energy calculation?}
Extensive explanation for the checklist questions can be found in Section~\ref{sec:step2}.
\begin{itemize}
\item First thing
\item Also remember
\item And finally
\end{itemize}
\end{checklist}

\begin{checklist}{Analysis}
\textbf{This is all about analysis of the simulation}
Extensive explanation for the checklist questions can be found in Section~\ref{sec:step4}.
\begin{itemize}
\item Are my simulations converged enough?
\item Am I using the right analysis techniques?
\end{itemize}
\end{checklist}

\end{Checklists*}
\clearpage

\section*{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
\todo[inline, color={green!20}]{ASJSM: @everyone, can you check your contribution is acknowledge and if not add the appropriate information. }
(Explain the contributions of the different authors here)
ASJSM: Coordinated the document, contributed to most sections, and created figures \ref{fig:fig2_what_is_lambda},~\ref{fig:fig7_sampling_scheme},~\ref{fig:overlap} and replotted~\ref{fig:automatic-equilibration-detection} 
JS: created figures \ref{fig:fig1_what_is_alchemy}, \ref{fig:fig3_binding-thermodynamic-cycle}-\ref{fig:fig6_absolute-thermodynamic-cycle}, the checklist and contributed to general formatting discussions.

% We suggest you preserve this comment:
For a more detailed description of author contributions,
see the GitHub issue tracking and changelog at \githubrepository.
